\documentclass[12pt,apa,article,oneside,strict,titlepage]{eyered}
\usepackage{eyered} % for information on eyerdoc packages, see http://www.eyer.us/eyerdoc
\include{man3301}

\author{Chad Michael Eyer}
\title{Discussion 1}
\runninghead{Discussion 1}
\date{2017-01-14}

% Preamble and document properties (end)

\begin{document} % start of document (fold)
% version control and frontmatter (fold)

\settitle % sets the document title and other relevant information

%\begin{abstract}
%	Place abstract text here...
%\end{abstract}

\settitle % sets the document title after the title page
% version control and frontmatter (end)

\section{\texorpdfstring{Discussion on Chapter 1
\autocite{decenzo2013fundamental-of-human-resource}}{Discussion on Chapter 1 {[}@decenzo2013fundamental-of-human-resource{]}}}\label{discussion-on-chapter-1-decenzo2013fundamental-of-human-resource}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  In the past fifty years, multinational corporations have become more
  common. Multinational corporations are global businesses that operate
  in multiple countries at the same time, each country with different
  populations and cultures. economic, ethical, and legal environments
  that often vary widely from one another. Human resource managers'
  careful consideration of the diverse demographics of these countries,
  together with the diverse economic, ethical, and legal environments
  (be they pronounced or subtle), is key to success in a global
  marketplace.
\item
  The advance of technology has propelled commerce throughout modern
  history. The most recent era of globalization (beginning ca. 2000 with
  the rise of the Internet) has been shaped by rapid and inexpensive
  exchange of people, products, and ideas around the globe. The global
  sharing of ideas and information requires a new kind of ``knowledge
  worker'' that have adapted their existing professions or created new
  professions to manage information technology. These advances empower
  human resource managers to communicate with, train, motivate, and
  manage data about current and prospective employees in real-time
  around the globe, with all the potential risks and liabilities that
  come with such power.
\item
  The accommodation, not assimilation, of workers with diverse
  abilities, backgrounds, experiences, and skills is necessary as
  businesses recruit from a more heterogeneous workforce and do business
  in the global marketplace. Human resource managers are tasked with
  creating a corporate culture that embraces diversity, while managing
  accountability to that culture and compliance with applicable laws and
  norms. This concept of accommodating employees as individuals often
  means a shift from treating all employees (and potential employees) as
  alike, and instead, intentionally working with the differing needs of
  individuals.
\item
  Employees do not leave their individual values at the door when
  reporting for work, and for a growing number of employees, those
  values include the importance of family, recreation, and personal
  goals, often above professional goals. Ubiquitous global communication
  both helps and hinders the idea of balance between work and life
  goals, allowing employees flexibility in when, where, and how
  employees work, and allowing employers to be more demanding of when,
  where, and how employees work. Human resource managers who create aa
  positive culture around work/life balance will give their companies a
  competitive edge in employee recruitment and retention.
\item
  Knowledge workers use information (usually facilitated by technology)
  in decision making. Human resource managers must continue to recruit
  with purpose, adapting to new technologies in advertising positions
  and résumé management, while selecting employees with both the
  ``hard'' skills necessary for success in a role and the ``soft''
  skills and attitude necessary to fit the culture of a team or company.
  Once hired, human resource managers must keep knowledge workers
  engaged and productive, a challenge given their productivity often
  cannot be measured in sales figures or widget production.
  Additionally, human resource managers must maintain a culture of
  productivity within the context of work/life balance when knowledge
  work is not necessarily tied to a traditional nine-to-five workday in
  a traditional office.
\item
  Companies seek efficiencies in all areas, including labor costs. Human
  resource managers play a role in maintaining employee morale and
  maximizing worker productivity through effective communication and
  management of employee retraining, compensation changes, workforce
  reductions through attrition, workforce reductions through layoffs,
  ``offshoring'' of work, automation of work, and mergers with and
  acquisitions of other companies. During recessions or other
  unfavorable economic conditions, human resource managers can
  effectively become the ``voice'' of a company to its workers and,
  through them, the public.
\item
  A contingent workforce (workers employed on a part-time, temporary,
  contract, or other as-needed basis) is an efficiency that helps human
  resource managers control labor costs. This workforce is managed in
  such a way to maximize flexibility for a company, allowing it to
  quickly respond to demand during peak times or for specialized
  projects and skills. From a human resource management perspective,
  contingent workers are often treated differently by company policy
  (especially policy concerning compensation), labor law, union
  contracts, and tax code than their full-time counterparts with whom
  they may work side-by-side. Additionally, human resource managers must
  effectively recruit, train, retain, and manage contingent workers
  while not disrupting its regular workforce or the culture of a
  company.
\item
  Employee empowerment allows individual employees or teams to respond
  to changing business conditions by contributing to decision making
  processes, often allowing for greater creativity in problem solving.
  Additionally, empowered employees feel part of their organization,
  increasing employee interest in a company's success. To be effective,
  this kind of employee engagement requires interpersonal and leadership
  skills in all employees. Human resource managers must recruit and
  train with these skills on mind.
\item
  A company's code of ethics defines its notions of right and wrong.
  Note that right, wrong, and legal are three overlapping concepts, but
  that legal does not necessarily imply ``right'' and illegal does not
  necessarily imply ``wrong.'' In both internal and external matters,
  companies are judged favorably or unfavorably by weighting their
  conduct against their ethical codes (as well as compliance with
  applicable laws, including the Sarbanes-Oxley Act). Personally and
  professionally, I value integrity highly. For this reason, I am
  fortunate to work for a company (Apple, Inc.) whose semiannual
  ``Business Conduct'' training invokes a quote attributed to Martin
  Luther King, Jr.: ``The time is always right to do what's right.''
\end{enumerate}

\clearpage
\setpagenotes
\clearpage
\setreferences % typesets the reference list; if no references are used, the list will not be typeset

% backmatter (end)

\end{document} % (end)

% end assignment_6.tex

